TGI-spinal-power

### 2022-06-21 analysis/tgispine_zoib_power-sim.Rmd
Gosia changes

# setting working directory
datPath <- '/home/alexm/sTGI/'
knitr::opts_knit$set(root.dir = datPath)
```

@@

# to run zero inflated regressions need to make sure no values = 100, as cannot model them, so simply minus a very small fraction from those values
df_VAS$beta <- ifelse(df_VAS$rating==100, df_VAS$beta-0.0001, df_VAS$beta <- df_VAS$rating)

@@

# Proportion zero function
Replaces proportion of data with zero, based on proportions for each condition calculated from pilot data - used in the simulation
```{r}
set.seed(1)
prop_zero <- function(x, vas = c('cold','warm','burn')) {
  x2 <- data.frame()
  # randomly generate two numbers around a normal distribution of 0, with a standard deviation of .03
  r <- rnorm(2, mean=0, sd=.05)
  if (vas[1] == 'cold'){
    x1 <- x %>%  filter(quality == 'cold')
    # add this number to the proportion of zeros calculated for each quality & stimuli from pilot data, for each participant
    zp_cnt <- CNTc_zero$prop[2] + r[1] 
    zp_tgi <- TGIc_zero$prop[2] + r[2]
    # adding if loop to make sure zp does not reach 0
    if (isTRUE(zp_cnt < 0)){
      zp_cnt = 0
    }
    if (isTRUE(zp_tgi < 0)){
      zp_tgi = 0
    }
    # turn zp into the proportion of total columns
    zp_cnt <- round(zp_cnt*nrow(filter(x1, stimuli == 'non-tgi')))
    zp_tgi <- round(zp_tgi*nrow(filter(x1, stimuli == 'tgi')))

>>>>

# setting working directory
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw'
knitr::opts_knit$set(root.dir = datPath)
```

@@

# to run zero inflated regressions need to make sure no values = 100, as cannot model them, so simply minus a very small fraction from those values
df_VAS$beta <- ifelse(df_VAS$rating==100, df_VAS$rating-0.0001, df_VAS$rating)

@@

# Proportion zero function
Replaces proportion of data with zero, based on proportions for each condition calculated from pilot data - used in the simulation
```{r}
set.seed(326) #is this needed?
prop_zero <- function(x, vas = c('cold','warm','burn')) {
  x2 <- data.frame()
  # randomly generate two numbers around a normal distribution of 0, with a standard deviation of .05
  r <- rnorm(2, mean=0, sd=.05)
  if (vas[1] == 'cold'){
    x1 <- x %>%  filter(quality == 'cold')
    # add this number to the proportion of zeros calculated for each quality & stimuli from pilot data, for each participant
    zp_cnt <- CNTc_zero$prop[2] + r[1] 
    zp_tgi <- TGIc_zero$prop[2] + r[2]
    # adding if loop to make sure zp does not reach 0
    if (isTRUE(zp_cnt < 0)){
      zp_cnt = 0
    }
    if (isTRUE(zp_tgi < 0)){
      zp_tgi = 0
    }
    # turn zp into the proportion of total columns
    zp_cnt <- round(zp_cnt*nrow(filter(x1, stimuli == 'non-tgi')))
    zp_tgi <- round(zp_tgi*nrow(filter(x1, stimuli == 'tgi')))
